---
title: "Simple Deduplication"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simple Deduplication}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## **Setup**

First, install and load the ASySD package.

```{r setup}
# devtools::install_github("camaradesuk/ASySD")
library(ASySD)
```

## **Loading Citation Data**

Begin by loading your citation data from an Endnote XML file using the **`load_search()`** function. You can specify alternative file formats such as CSV if needed.

```{r}
citations <- load_search("systematic_search.xml", method="endnote")
```

## Automated deduplication

Remove duplicate citations automatically using the `dedup_citations` function.

```{r}
results <- dedup_citations(citations, merge_citations = TRUE)
```

The `dedup_citations` function returns a list of two dataframes by default. The first contains unique citations after duplicates were removed automatically by ASySD. In most cases, this will remove the vast majority of duplicates. There will likely be some duplicates remaining which need manual review by a human (see next step).

```{r}
unique_citations <- results$unique
```

## Manual deduplication

To address remaining duplicates, review potential pairs manually. You can examine them within R or export them to a CSV or Excel file for detailed inspection.

```{r}
potential_duplicates <- results$manual_dedup
```

Review the pairs using the `manual_dedup_shiny()` function. This opens up and interactive shiny app to allow you to go through each potential duplicate pair. Save the output to an object so you can use it later. Once complete, the result column will show the matches and non matches. Retain the matches for the next step.
```{r eval=FALSE}
post_manual_review <- manual_dedup_shiny(potential_duplicates) 
post_manual_review <- post_manual_review %>%
  filter(result=="match")
```

## **Final Deduplication**

Combine the results of automated and manual deduplication using the `dedup_citations_add_manual()` function. Include any additional duplicates you've identified in the `additional_pairs` argument.

```{r eval=FALSE}
final_results <- dedup_citations_add_manual(unique_citations, additional_pairs = post_manual_review)
```

## **Exporting Results**

You can now write your results to a file for import into a reference manager or systematic review software

```{r eval=FALSE}
write_citations(final_results, type="txt", filename="citations.txt")
```
